This chapter outlines the general features of the \texttt{\getsoftwarename{}} application. We show when the features were introduced and what features and when you can expect to see in the future. This provides a roadmap of where this application has come from and where it is headed. The future features are highly dependent on user feedback. You are highly encouraged to contact us to discuss any new features you would like to see in the application.\\

\Cref{tab:schedule} shows the scheduled release dates for this tool and includes the list of features provided in that release or what you can expect to see in future releases. The individual feature requirements are outlined in \Cref{tab:featureRequirements}. If you would like some additional features added, please contact us.
Additionally, we would appreciate any feedback on this tool. An anonymous
user survey is available \insertsurveylink{here}. \\

\begin{table}[hbt!]                    
  \centering
\begin{adjustbox}{max width=\textwidth}            
  \begin{tabular}{lll}                    
    \toprule          
      Version & 	Release	 & Requirements \\  \hline
      2.0	 & October 2019 & 1.1, 1.2, 2.1, 2.2, 3.1, 3.6, 4.1, 4.2, 4.3, 4.1, 4.2, 4.3, 5.1, 7, 8.1, 9.1\\  \hline
  \end{tabular}
\end{adjustbox}
  \caption{Schedule of Release}             
  \label{tab:schedule}                 
\end{table}


\newpage
\begin{longtable}{| p{.05\textwidth} | p{.75\textwidth} | p{.08\textwidth} | p{.08\textwidth} |}
    \toprule
      \# & Description & Priority & Version \\ \hline
      1 & \textbf{Forward Uncertainty Propagation} &  &  \\ 
	1.1 & Input uncertainty characterization & M & 2.0 \\ \hline
	1.2 & PDF Approximation & M & 2.0 \\ \hline
	1.3 &  Descriptive output statistics & M & 2.0 \\ \hline
	1.4 &  Basic Monte Carlo Sampling  & M & 2.0 \\ \hline	
	1.5 &  Importance Sampling for rare events  & M & 2.0 \\ \hline	
	1.6 &  Cross-Entropy sampling  & M & 2.0 \\ \hline
	1.7 &  Surrogate modeling, Gauss. Pr. Models  & M & 2.0 \\ \hline
	1.8 &  Surrogate modeling, Pol. Ch. Models  & M & 2.0 \\ \hline
	1.9 &  Multi-fidelity sampling  & M & 2.0 \\ \hline
	1.10 &  Spatial/temporal stochastic models  & M & 2.0 \\ \hline
	1.11 &  CCDF estimation for rare events  & M & 2.0 \\ \hline
	2 & \textbf{Sensitivity Analysis} &  &  \\ \hline
	2.1 & Global sensitivity Sobol's indices & M & 2.0  \\ \hline
	3 & \textbf{System Identification and Bayesian Inference} &  & 2.0 \\ \hline
	3.1 & Parameter estimation & M & 2.0 \\ \hline
	3.1 & Basic Bayesian parameter updating & M & 2.0 \\ \hline
	3.1 & Advanced MCMC-based Bayesian updating & M & 2.0 \\ \hline
	3.2 & Advanced Surrogate-based Bayesian updating & D & 2.0 \\ \hline
	3.3 & Model class selection & D & 2.0 \\ \hline
	3.3 & Sequential Bayesian updating & D & 2.0 \\ \hline
	4 & \textbf{Optimization under Uncertainty} &  &  \\ \hline
	4.1 & Reliability-Based Design Optimization & M & 2.0 \\ \hline
	4.2 & Single-objective optimization under uncertainty & M & 2.0 \\ \hline
	4.3 & Multi-objective optimization under uncertainty & M & 2.0 \\ \hline
	5 & \textbf{Reliability Analysis} &  &  \\ \hline
	5.1 & First/Second Order Reliability Methods & M & 2.0 \\ \hline
	5.2 & Local/Global reliability & M & 2.0 \\ \hline
	\bottomrule
\caption{Feature Requirements (M=Mandatory, D=Desirable, O=Optional, P=Possible Future)}             
  \label{tab:featureRequirements}                 
\end{longtable}
