The audience of the tool are researchers/Practitioners trying to predict the response of a structure to earthquakes.

This open-source research application (\href{https://github.com/NHERI-SimCenter/EE-UQ}{https://github.com/NHERI-SimCenter/EE-UQ}) 
provides an application researchers can use to predict the response of a building subjected to earthquake events. The application is focused 
on quantifying the uncertainties in the predicted response, given the that the properties of the buildings and the earthquake events are not known exactly, 
and that the simulation software and the user make simplifying assumptions in the numerical modeling of that structure. In the application, 
the user is required to characterize the uncertainties in the input. The application will after utilizing the selected sampling method, 
will provide information that characterizes the uncertainties in the response measures. The computations to make these determinations 
can be prohibitively expensive. To overcome this impediment the user has the option to perform the computations on the Stampede2 
supercomputer. Stampede2 is located at the Texas Advanced Computing Center and made available to the user through NHERI DesignSafe, 
the cyberinfrastructure provider for the distributed NSF funded Natural Hazards in Engineering Research Infrastructure (NHERI) facility.\\

The computations are performed in a workflow application. That is, the numerical simulations are actually performed by a number of 
different applications. The EE-UQ backend software runs these different applications for the user, taking the outputs from some programs 
and providing them as inputs to others. The design of the EE-UQ application is such that researchers are able to modify the backend 
application to utilize their own application in the workflow computations. This will ensure researchers are not limited to using the 
default applications we provide and will be enthused to provide their own applications for others to use. \\

This is Version 1.0 of the tool and as such is limited in scope. Researchers are encouraged to comment on what additional features and 
applications they would like to see in this application. If you want it, chances are many of your colleagues also would benefit from it.\\
\\
